Spectral Lags in Very High Energy Emission of Gamma Ray Bursts

### 2013-11-25 gammaRays.tex
computed kappa sample to 250 points
added observations to distirbution plots

For our set of parameters, this algorithm produced a sample, empirical CDF of which you can see on fig. However, the error margins of the observed stretching factors are too large to use the KS-test on them. Nevertheless, It appears that our model doesn't contradict existing observations.

>>>>

\begin{figure}[kappaDistribution]
        \centering
        \begin{subfigure}[kappaDistributionHistogram]{0.49\textwidth}
                \includegraphics[width=\textwidth]{kappaDistributionHistogram}
                \label{fig:kappaDistributionHistogram}
        \end{subfigure}
        \begin{subfigure}[kappaDistributionCDF]{0.49\textwidth}
                \includegraphics[width=\textwidth]{kappaDistributionCDF}
                \label{fig:kappaDistributionCDF}
        \end{subfigure}
        \caption{The histogram and the CDF of the stretching factors sample produced by our model (blue). The sample contains $250$ points. The red curve is an empirical CDF of the observed sample (3 points).}
        \label{fig:kappaDistribution}
\end{figure}

Our set of parameters led to a sample you can see on the figure \ref{fig:kappaDistribution}. However, the error margins of the observed stretching factors are too large to use the KS-test on them. Nevertheless, It appears that our model doesn't contradict existing observations.
